% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
%
%   http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.

\subsection{Traffic Routers}

\subsubsection{CDN}
The CDN to which a Traffic Router belongs is represented by its Name, which
uniquely identifies it. The Traffic Router MUST be an/the authoritative DNS
server for the Domain of the CDN to which it belongs.

\subsubsection{Domain}
This is the "domain" part of the Cache Server's Fully Qualified Domain Name
(FQDN) as a string. For example, a Cache Server with an FQDN of
\code{github.com} has a Domain of \code{com} and a Cache Server with an FQDN of
\code{trafficcontrol.apache.org} has a Domain of \code{apache.org}.

\subsubsection{Host Name}
This is the "host" part of the Cache Server's Fully Qualified Domain Name (FQDN)
as a string. For example, a Cache Server with an FQDN of \code{github.com} has a
Host Name of \code{github}, and a Cache Server with an FQDN of
\code{trafficcontrol.apache.org} has a Host Name of \code{trafficcontrol}.\\
This field does NOT need to be unique, though operators are encouraged to make
this - or at least the concatenation \code{\emph{Host Name}.{Domain}} - unique
for ease of operation.

\subsubsection{ID}
A Cache Server's "ID" is an unsigned integer that uniquely identifies it among
all Cache Servers. It serves no purpose beyond unique identification of the
Cache Server.

\subsubsection{Notes}
This section is an arbitrary string containing miscellaneous, human-friendly
information about the Cache Server. Other ATC components SHOULD NOT parse this
for specific information fields, or expect it to be in a particular format.

\subsubsection{Physical Location}
The Physical Location at which a Cache Server resides is represented by a string
containing its Name.
