% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
%
%   http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.

\subsection{Users\label{sec:users}}
A user represents a person who may be authenticated with the Traffic Ops API and
their ability to interact with Traffic Ops Data Model objects. A User object
also contains "meta" information such as their email address.

\subsubsection{Address}
This is a text field with no defined structure, but semantically it represents a
user's real-world, physical address. If it is not an empty value, it is assumed
to contain enough information to send a letter through normal postage to the
user.\\
Addresses may consist of alphanumeric characters, hyphens, periods, spaces, and
newlines, but may not end with a space or newline.

\subsubsection{Email}
A user's email address, which is used for initial registration and password
recovery. A User object is not guaranteed to have an Email because the initial,
default User will not have one. However, UIs based on the Traffic Ops API are
encouraged to require that new users have one, as otherwise they will be unable
to recover their account if their password is forgotten.\\
Emails are unique among all Users, unless they are "Null"-valued.\\
Representation formats that do not support email addresses natively as a type
MUST represent this a string.

\subsubsection{Full Name}
A user's "full" name, as it would appear on a letter mailed to them, as a
string. This field, if not empty, is presumed to be the user's name as it would
appear on normal postage. This field MUST NOT be allowed to contain
non-alphabetic characters.

\subsubsection{Phone Number}
A string which, if not empty, is presumed to be a telephone number at which the
user may be contacted. It MUST only be allowed to contain numerics and hyphens,
and must neither start nor end with a hyphen.

\subsubsection{Role}
A user's permissions are encapsulated by their Role, which is represented as a
map containing two keys, "name" that maps to the Role's Name as a string and
"permissions" which maps to a set of Permission Names as strings.

\subsubsection{Tags}
The Tags associated with a User are represented by a set of strings that are
Tag Names.\\
Note that Tags \emph{cannot be used to control a User's access to or ability to
interact with \textbf{anything}}. These are controlled entirely by a User's
Tenant and Role.

\subsubsection{Tenant}
The scope of a user's permissions is expressed as a string that is the Name of
the Tenant to which the user belongs.

\subsubsection{Username}
A user's "Username" is a string that is used to uniquely identify them among all
Users. It is only allowed to contain alphanumeric characters.
