% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
%
%   http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.

\subsection{Physical Location}
Physical Locations are exactly what they sound like, a real, physical place
where component hardware is stored.\\
Mainly this contains metadata for support purposes, but it can also be used
to provide some routing fallback behavior.

\subsubsection{Address}
This is a text field with no defined structure, but semantically it represents
a Physical Location's real-world, physical address. If it is not an empty
value, it is assumed to contain enough information to send a letter through
normal postage to the Physical Location (though the site may not actually be
capable of receiving mail).\\
Addresses may consist of alphanumeric characters, hyphens, periods, spaces, and
newlines, but may neither begin nor end with a space or newline.

\subsubsection{Email}
A string that contains an email address (unless it is an empty string) which is
used for communicating with the Physical Location's "Point of Contact".

\subsubsection{Name}
A string that uniquely identifies the Physical Location. It MUST only contain
alphanumeric characters and spaces, but may neither begin nor end with a space.

\subsubsection{Notes}
This string has no defined structure or semantic meaning and is used to contain
miscellaneous information.

\subsubsection{Phone Number}
A string which, if not empty, is presumed to be a telephone number at which the
Physical Location's "Point of Contact" may be contacted.\\
It may only contain numerics and hyphens, and may neither start nor end with a
hyphen.

\subsubsection{Point of Contact Name}
A string which, if not empty, is presumed to be the proper name of the
designated "Point of Contact" for the Physical Location.\\
This may contain alphabetic character, periods, hyphens, spaces, commas, and
apostrophes, but may neither begin nor end with a hyphen or a space.
