% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
%
%   http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.

\subsection{Traffic Stats Servers}
Traffic Stats Servers are instances of Traffic Stats and contain information
relating to their network connection information as well as configuration.

\subsubsection{All Graph URL}
This string is a URL that is the location of a Grafana dashboard that aggregates
Delivery Service-level statistics. If it is "null"-typed, then components will
assume that such a dashboard is unavailable (either because no connected Grafana
instance exists or because it simply does not provide the dashboard).

\subsubsection{Cache Group Graph URL}
This string is a URL that is the location of a Grafana dashboard that provides
statistics for one or more Cache Groups (chosen via a 'which' query string
parameter). If it is "null"-typed, then components will assume that such a
dashboard is unavailable (either because no connected Grafana instance exists or
because it simply does not provide the dashboard).

\subsubsection{Cache Server Graph URL}
This string is a URL that is the location of a Grafana dashboard that provides
statistics for one or more Cache Servers (chosen via a 'which' query string
parameter). If it is "null"-typed, then components will assume that such a
dashboard is unavailable (either because no connected Grafana instance exists or
because it simply does not provide the dashboard).

\subsubsection{CDN}
This is a string that is the Name of the CDN to which the Traffic Stats Server
belongs.

\subsubsection{Delivery Service Graph URL}
This string is a URL that is the location of a Grafana dashboard that provides
statistics for one or more Delivery Services (chosen via a 'which' query string
parameter). If it is "null"-typed, then components will assume that such a
dashboard is unavailable (either because no connected Grafana instance exists or
because it simply does not provide the dashboard).

\subsubsection{Domain}
The "domain" part of the Traffic Stats Server's Fully Qualified Domain Name
(FQDN) as a string. For example, a Traffic Stats Server with an FQDN of
\code{github.com} has a Domain of \code{com} and a Traffic Stats Server with an
FQDN of \code{trafficcontrol.apache.org} has a Domain of \code{apache.org}.\\
In other words, this is every part of the Traffic Stats Server's FQDN that
isn't part of its Host Name.

\subsubsection{Host Name}
This is the "host" part of the Traffic Stats Server's Fully Qualified Domain
Name (FQDN) as a string. For example, a Traffic Stats Server with an FQDN of
\code{github.com} has a Host Name of \code{github}, and a Traffic Stats Server
with an FQDN of \code{trafficcontrol.apache.org} has a Host Name of
\code{trafficcontrol}.\\
In other words, a Traffic Stats Server's Host Name is the only part of its FQDN
that is not part of its Domain.\\
This field does NOT need to be unique, though operators are encouraged to make
this - or at least the concatenation \code{\emph{Host Name}.\emph{Domain}} -
unique for ease of operation.

\subsubsection{ID}
An integral, unique identifier for the Traffic Stats Server. It carries no
meaning or significance beyond being a unique identifier.

\subsubsection{Notes}
This is a string of arbitrary text for miscellaneous purposes.

\subsubsection{Physical Location}
This string gives the Name of a Physical Location within which this Traffic
Stats Server resides. If this is "null"-typed value, then it is understood that
the Traffic Stats Server has no well-defined and/or meaningful Physical
Location.

\subsubsection{Visual Status Panel 1}
This string is a URL that is the location of a Grafana dashboard that provides
CDN-level statistics, and in particular provides some kind of visual "status"
identifier for a CDN or CDNs. If it is "null"-typed, then components will assume
that such a dashboard is unavailable (either because no connected Grafana
instance exists or because it simply does not provide the dashboard).
