% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
%
%   http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.

\subsection{Traffic Ops Servers}
A Traffic Ops server is a server on which a Traffic Ops instance is running. It
contains information regarding its configuration as well as server properties.

\subsubsection{Domain}
The "domain" part of the Traffic Ops Server's Fully Qualified Domain Name (FQDN)
as a string. For example, a Traffic Ops Server with an FQDN of \code{github.com}
has a Domain of \code{com} and a Traffic Ops Server with an FQDN of
\code{trafficcontrol.apache.org} has a Domain of \code{apache.org}.\\
In other words, this is every part of the Traffic Ops Server's FQDN that isn't
part of its Host Name.

\subsubsection{Host Name}
This is the "host" part of the Traffic Ops Server's Fully Qualified Domain Name
(FQDN) as a string. For example, a Traffic Ops Server with an FQDN of
\code{github.com} has a Host Name of \code{github}, and a Traffic Ops Server
with an FQDN of \code{trafficcontrol.apache.org} has a Host Name of
\code{trafficcontrol}.\\
In other words, a Traffic Ops Server's Host Name is the only part of its FQDN
that is not part of its Domain.\\
This field does NOT need to be unique, though operators are encouraged to make
this - or at least the concatenation \code{\emph{Host Name}.\emph{Domain}} -
unique for ease of operation.

\subsubsection{ID}
An integral, unique identifier for the Traffic Ops Server. It carries no meaning
or significance beyond being a unique identifier.

\subsubsection{Notes}
This is a string of arbitrary text for miscellaneous purposes.

\subsubsection{Online}
This boolean value indicates whether or not the Traffic Ops Server is online
and/or currently serving its main service.

\subsubsection{Port}
This unsigned integer defines the Port on which the Traffic Ops Server is
listening. This MUST NOT be equal to or greater than $2^{16}$ ($65,536$).
